Probabilities of polar aligned disks in binary star systems

### 2024-08-22 src/tex/ms.tex
Write a bit about K-L

>>>>

To interpret the Kozai-Lidov oscillations in this limit we can picture a system from the point of view of a far-away stationary observer. When $j \approx 0$, the orbital parameters of the interior binary are not effected by the disk, and the disk undergoes precession or libration due to the effects of the binary. When $j$ is high, however, it is the disk that appears static. An observer would see oscillations in the orbital parameters of the central binary, and its angular momentum and eccentricity vectors would change in response to the disk. This can be thought of in terms of the classical Kozai-Lidov problem, where instead of a planet and its satellite, the interior objects are the binary, and the exterior perturbing object is the circumbinary disk.

\TJ{Does this explain why we see prograde precession when $i=\pi$ for high $j$. Will prograde precession of an anti-aligned disk lead to alignment?}
